The promise of community driven preprints in ecology and evolution

### 2024-04-18 ms/ms.qmd
awknowledgemets

Authors: Daniel W.A. Noble, Shinichi Nakagawa, Hackathon Participants, Malgorzata Lagisz

@@

>>>>

Authors: Daniel W.A. Noble ^1^ $\ddagger$, Shinichi Nakagawa^2^, Hackathon Participants, Malgorzata Lagisz^2^

Affiliations:
^1^ Division of Ecology and Evolution, Research School of Biology, The Australian National University, Canberra, ACT 2600, Australia &NewLine;  
^2^ Ecology and Evolution Research Centre, School of Biological, Earth and Environmental Sciences, University of New South Wales, Sydney, NSW, Australia &NewLine;

$\ddagger$ corresponding author, daniel.noble@anu.edu.au &NewLine;

@@

# Awknowledgements
We would like to thank the California Digitial Library (CDL) and the CDL team (particularly Alainna Wrigley) for their support in hosting and maintaining *EcoEvoRxiv* for the Society for Open, Reliable, and Transparent Ecology and Evolution (SORTEE). We would also like to thank Gabriela Hidalgo, Daisy Larios
for helping connect us with the IUCN and facilitating discussions to make *EcoEvoRxiv* a place where IUCN reports can be posted. Finally, we would also like to thank the endless number of SORTEE volunteers, and those especially on the *EcoEvoRxiv* Commitee, who have helped to make *EcoEvoRxiv* a success. This paper emerged from a hackathon at the 2022 SORTEE conference, and we thank delegates who attended the session but could not be part of this paper. DWAN would also like to thank the Australian Research Council Future Fellowship support (FT220100276).
